Blueprint

### 2020-11-24 blueprint.tex
Updates blueprint

\begin{cons}
	Let $S$ be a multiplicative submonoid of $R$. We consider pairs $(r, s)$ with $r \in R$ and $s \in S$ and we define the following relation on them
	\[
	(r, s) \sim (r', s')
	\]
	if and only if there exists $s_1 \in S$ such that $s_1(s' r - s r') = 0$. One checks that the relation $\sim$ is an equivalence relation. The equivalence class of a pair $(r, s)$ is denoted by $r/s$ and the set of equivalence classes is denoted by $S^{-1} R$. We define the following addition on $S^{-1} R$.
	\[
	\frac{r}{s} + \frac{r'}{s'} = \frac{r s' + r' s}{s s'}
	\]
	We also define the following multiplication on $S^{-1} R$. 
	\[
	\frac{r}{s} \times \frac{r'}{s'} = \frac{r r'}{s s'}
	\]
\end{cons}

@@

\begin{cons}
	Let $U$ be an open subset of Spec $R$. We define $\mathscr{O}(U)$ to be the set of all functions 
	\[
	s: U \rightarrow \bigcup \limits_{\mathfrak{p} \in U} R_{\mathfrak{p}}
	\]
	such that $s(\mathfrak{p}) \in R_{\mathfrak{p}}$ for every $\mathfrak{p} \in U$ and such that for every $\mathfrak{p} \in U$, there exist a neighborhood $V$ of $\mathfrak{p}$, contained in $U$, and elements $r, f \in R$, such that for each $\mathfrak{q} \in V$, $f \notin \mathfrak{q}$ and $s(\mathfrak{q}) = r/f$.  
\end{cons}

>>>>

\begin{cons}
	Let $S$ be a multiplicative submonoid of $R$. We consider pairs $(r, s)$ with $r \in R$ and $s \in S$ and we define the following relation on them
	\[
	(r, s) \sim (r', s')
	\]
	if and only if there exists $s_1 \in S$ such that $s_1(s' r - s r') = 0$. One checks that the relation $\sim$ is an equivalence relation. The equivalence class of a pair $(r, s)$ is denoted by $r/s$ and the set of equivalence classes is denoted by $S^{-1} R$. \\
	We define the following addition on $S^{-1} R$.
	\[
	\frac{r}{s} + \frac{r'}{s'} = \frac{r s' + r' s}{s s'}
	\]
	We also define the following multiplication on $S^{-1} R$. 
	\[
	\frac{r}{s} \times \frac{r'}{s'} = \frac{r r'}{s s'}
	\]
\end{cons}

@@

\begin{cons}
	Let $U$ be an open subset of Spec $R$. We define $\mathscr{O}(U)$ to be the set of all functions 
	\[
	s: U \rightarrow \bigcup \limits_{\mathfrak{p} \in U} R_{\mathfrak{p}}
	\]
	such that $s(\mathfrak{p}) \in R_{\mathfrak{p}}$ for every $\mathfrak{p} \in U$ and such that for every $\mathfrak{p} \in U$, there exist a neighborhood $V$ of $\mathfrak{p}$, contained in $U$, and elements $r, f \in R$, such that for each $\mathfrak{q} \in V$, $f \notin \mathfrak{q}$ and $s(\mathfrak{q}) = r/f$. \\
	We endow $\mathscr{O}(U)$ with the sum and product of such functions and we take for the multiplicative unit the function that maps each $\mathfrak{p}$ on the multiplicative unit of $R_{\mathfrak{p}}$. \\
	Last, if $V \subseteq U$, then the morphism of rings $\mathscr{O}(U) \rightarrow \mathscr{O}(V)$ maps each $s \in \mathscr{O}(u)$ on its restriction $s \restriction V$. 
\end{cons}
